Modeling thermal dust emission in the {\it PLANCK} 2015 release maps

### 2015-06-20 ms.tex
outline
remove coloring from Table 2

@@

>>>>

\section{Data}
\label{sec:data}

\section{Preprocessing}
\label{sec:prepro}

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}

\subsection{Compact Sources}
\label{sec:ptsrc}

\subsection{Smoothing}
\label{sec:smth}

\subsection{Molecular Emission}
\label{sec:mole}

\subsection{Zero Level}
\label{sec:zp}

\subsubsection{Absolute Zero Level}
\label{sec:zp_abs}

\subsubsection{Relative Zero Level}
\label{sec:relzero}

\section{Dust Emission Model}
\label{sec:modeling}

\section{Predicting the Observed SED}
\label{sec:bpcorr}

\section{Global Model Parameters}
\label{sec:global}

\section{MCMC Fitting Procedure}
\label{sec:fitting}

\subsection{Pixelization}
\label{sec:pix}

\subsection{Sampling Parameters}
\label{sec:samp}

\subsection{Markov Chains}
\label{sec:mcmc}

\subsection{Low-resolution Fits}
\label{sec:lores}

\subsection{Global Parameters Revisited}
\label{sec:hier}

\section{Optical Reddening}
\label{sec:ebv}

\subsection{Reddening Calibration Procedure}
\label{sec:calib_ebv}

\subsection{Rectifying the Reddening Residuals}

\section{Comparison of Emission Predictions}
\label{sec:em_compare}

\subsection{The 353-3000 GHz Frequency Range}
\label{sec:hifreq}

\subsection{The 100-217 GHz Frequency Range}
\label{sec:lofreq}

\section{Data Release}
\label{sec:release}

\section{Conclusions}
\label{sec:conclusion}

\subsection{Single-MBB versus Two-component emission}

\subsection{Towards a Replacement for SFD}
\label{sec:replace}

@@

\begin{center}
\begin{deluxetable*}{llrrrrrrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{11} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters (2015 release)} 
\tablehead{
\colhead{Number} &
\colhead{Model} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$} &
\colhead{$T_2$} &
\colhead{$T_1$} &
\colhead{$n$} &
\colhead{D.O.F.} &
\colhead{$\chi^2$} &
\colhead{$\chi^2_{\nu}$}
}
\startdata
 1 & FDS99 best-fit  & 0.0363 & 13.0 & 1.67 & 2.70 & 15.67 & 9.12 & 1.055 & 7 & 55.0 & 7.86 \\
 2 & FDS99 general   & 0.0457 & 8.03 & 1.59 & 2.83 & 15.68 & 9.71 & 0.998 & 3 & 6.42 & 2.14 \\
 3 & single MBB      & 0.0    &  ... &  ... & 1.56 & 19.86 & ...  & 1.016 & 6 & 48.0 & 7.99 \\ %[-2ex]
\enddata
\end{deluxetable*}
\end{center}
